---
title: "Macroeconomic data"
author: "Claudius Gräbner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Macroeconomic data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Information about the data set

## Meta data
Here goes the documentation of the data set. Note that you can also look at `data-raw/macro_data.R` to see how the data gets constructed.


| Variable         | Description                                  | Unit                          | Source           |
| -----------------|:--------------------------------------------:| :----------------------------:|:----------------:|
| iso3c                   | The iso3 country code                                                                                       | iso3c    | [Info][1] |
| year                    | The year of observation                                                                                     |   NA     |  |
| res_rents               | Natural ressource rents                                                                                     | % of GDP | [World Bank][2]
| gdp_real_lcu            | Real GDP in constant LCU                                                                                    | constant LCU | [World Bank][3]
| gdp_real_lcu_growth     | Real GDP growth (constant LCU)                                                                              | % change | [World Bank][4]
| gdp_real_pc_lcu         | Real GDP per capita (constant LCU)                                                                          | constant LCU per capita | [World Bank][5]
| gdp_real_pc_lcu_growth  | Real GDP per capita growth (constant LCU)                                                                   | % change | [World Bank][6]
| gdp_real_usd            | Real GDP (constant 2010 US$)                                                                                | constant 2010 US$ | [World Bank][7]
| gdp_real_pc_usd         | Real GDP per capita (constant 2010 US$)                                                                     | constant 2010 US$ per capita | [World Bank][8]
| gdp_nom_lcu             | Nominal GDP (current LCU)                                                                                   | current LCU | [World Bank][9]
| gdp_nom_pc_lcu          | Nominal GDP per capita (current LCU)                                                                        | current LCU per capita | [World Bank][10]
| gdp_nom_usd             | Nominal GDP (current US$)                                                                                   | current US$ | [World Bank][11]
| gdp_nom_pc_usd          | Nominal GDP per capita (current US$)                                                                        | current US$ per capita | [World Bank][12]
| gdp_real_ppp            | GDP, PPP (constant 2011 int $)                                                                              | constant 2011 int $ | [World Bank][13]
| gdp_real_pc_ppp         | GDP, PPP per capita (constant 2011 int $)                                                                   | constant 2011 int $ per capita | [World Bank][14]
| gdp_nom_ppp             | GDP, PPP (current int $)                                                                                    | current int $ | [World Bank][15]
| gdp_nom_pc_ppp          | GDP, PPP per capita (current int $)                                                                         | current int $ per capita | [World Bank][16]     
| cpi                     | Harmonised consumer price index (all items)                                                                 | 2015 = 100           | [AMECO][16]       |
| unemp_rate              | Unemployment rate                                                                                           | % of active population | [AMECO][16]     |
| cap_form                | Gross fixed capital formation, total economy                                                                | current prices       | [AMECO][16]       |
| wage_share              | Adjusted wage share                                                                                         | % of GDP             | [AMECO][16]       |
| rulc                    | Real unit labour costs: total economy (Ratio compensation per employee to nominal GDP per pers employed.)   | 2010=100             | [AMECO][16]       |
| nulc_nac                | Nominal unit labour costs: total economy (Ratio compensation per employee to real GDP per pers employed.)   | Loc curr: 2010 = 100 | [AMECO][16]       |
| nulc_eur                | Nominal unit labour costs: total economy (Ratio compensation per employee to real GDP per pers employed.)   | EUR: 2010 = 100      | [AMECO][16]       |
| eci_harv                | Economic Complexity Index (ECI)           | Index | [Harvard][17] |
| eci_rank_harv           | Rank of the country according to the ECI  | Index | [Harvard][17] |
| eci_mit                | Economic Complexity Index (ECI)           | Index | [MIT][18] |
| eci_rank_mit           | Rank of the country according to the ECI  | Index | [MIT][18] |
| current_account_GDP_WB           | Sum of net exports of goods and services, net primary income, and net secondary income.  | % of GDP | [World Bank][19] |
| current_account_GDP_ameco           | Sum of net exports of goods and services, net primary income, and net secondary income.  | % of GDP | [AMECO][16] |
| population           | Total population (midyear estimates).  | % of GDP | [World Bank][20] |
| debt_corp_nf_percGDP  | Debt of non-financial corporations (`DBTS11GDP`).  | % of GDP | [OECD (FIN_IND_FBS)][21]|
| debt_corp_f_percGDP   | Debt of financial corporations (`DBTS12GDP`).  | % of GDP | [OECD (FIN_IND_FBS)][21]|
| debt_gen_gov_percGDP  | Debt of general government (`DBTS13GDP`).  | % of GDP | [OECD (FIN_IND_FBS)][21] |
| debt_hh_npish_percGDI | Debts of households and NPISHs (`DBTS14_S15GDI`).  | % of GDI | [OECD (FIN_IND_FBS)][21]|
| total_debt_percGDP    | Debt of the total economy (`DBTS1GDP`).  | % of GDP | [OECD (FIN_IND_FBS)][21] |
| empl_ind | Employment in industry | % of total employment | [World Bank][22] |
| empl_agr | Employment in agriculture | % of total employment | [World Bank][23] |
| empl_serv | Employment in services | % of total employment | [World Bank][24] |
| empl_self | Self-employed | % of total employment | [World Bank][25] |
| unemp_youth_neet | Share of youth not in education, employment of training |  % of youth population | [World Bank][26] |
| VA_industry_gdp | Value added of industry (including construction) |  % of GDP |  [World Bank][27] |
| VA_manufct_gdp | Value added of manufacturing | % of GDP |  [World Bank][28] |
| wgi_accountability | Voice and Accountability captures perceptions of the extent to which a country's citizens are able to participate in selecting their government, as well as freedom of expression, freedom of association, and a free media (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| wgi_control_corrupt | Control of Corruption captures perceptions of the extent to which public power is exercised for private gain, including both petty and grand forms of corruption, as well as "capture" of the state by elites and private interests (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| wgi_gov_effectvn | Government Effectiveness captures perceptions of the quality of public services, the quality of the civil service and the degree of its independence from political pressures, the quality of policy formulation and implementation, and the credibility of the government's commitment to such policies (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| wgi_pol_stability | Political Stability and Absence of Violence/Terrorism captures perceptions of the likelihood that the government will be destabilized or overthrown by unconstitutional or violent means, including politically-motivated violence and terrorism (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| wgi_rule_of_law | Rule of Law captures perceptions of the extent to which agents have confidence in and abide by the rules of society, and in particular the quality of contract enforcement, property rights, the police, and the courts, as well as the likelihood of crime and violence. (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| wgi_regul_quality | Regulatory Quality captures perceptions of the ability of the government to formulate and implement sound policies and regulations that permit and promote private sector development (this is the estimate, errors and percentiles are also [available][29]). | Index (-2.5 to 2.5) | WGI [home][29]  [API][30] |
| fdi_net_inflow_GDP | Foreign direct investment, net inflows | % of GDP |  [World Bank][31] | 
| fdi_net_outflow_GDP | Foreign direct investment, net outflows | % of GDP |  [World Bank][32] |  
| tax_rev_total_GDP | Tax revenue | % of GDP |  [World Bank][33] | 
| tax_rev_trade_TAX | Taxes on international trade | % of revenue |  [World Bank][34] | 
| tax_rev_inc_profits_TAX | Taxes on income, profits and capital gains | % of revenue |  [World Bank][35] | 
| trade_total_GDP | Trade is the sum of exports and imports of goods and services measured as a share of gross domestic product | % of GDP | [World Bank][36] |  
| trade_exp_GDP | Exports of goods and services | % of GDP |  [World Bank][37] | 
| trade_imp_GDP | Imports of goods and services | % of GDP |  [World Bank][38] | 
| RD_expend_GDP | Research and development expenditure | % of GDP |  [World Bank][39] | 
| RD_scientists | The number of researchers engaged in Research &Development (R&D) | Persons per per million people |  [World Bank][40] |
| interest_long_term | Interest rates of long term (in most cases 10 year) government bonds (`IRLT`). | Per cent | [OECD (MEI_FIN)][41] |
| average_wages | Average annual wages per full-time and full-year equivalent employee in the total economy. | 2017 USD PPPs| [OECD (AV_AN_WAGE)][42] |
| debt_gen_gvt_gross | Government gross debt-to-GDP ratio (`DBTS13GDP`). | % of GDP | [OECD (NAAG)][43] |
| school_agv_yrs | Average Years of Schooling Attained | Share of population over 15 | [Barro-Lee][44] |
| school_share_sec | Percentage of Complete Secondary Schooling Attained | Share of population over 15 | [Barro-Lee][44] |
| school_share_ter | Percentage of Complete Tertiary Schooling Attained | Share of population over 15 | [Barro-Lee][44] |

[1]: https://unstats.un.org/unsd/tradekb/knowledgebase/country-code
[2]: https://data.worldbank.org/indicator/ny.gdp.totl.rt.zs
[3]: https://data.worldbank.org/indicator/NY.GDP.MKTP.KN
[4]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KN
[5]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KD.ZG
[6]: https://data.worldbank.org/indicator/NY.GDP.MKTP.KD
[7]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KD
[8]: https://data.worldbank.org/indicator/NY.GDP.MKTP.CN
[9]: https://data.worldbank.org/indicator/NY.GDP.PCAP.CN
[10]:https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
[11]: https://data.worldbank.org/indicator/NY.GDP.PCAP.CD
[12]: https://data.worldbank.org/indicator/NY.GDP.MKTP.PP.KD
[13]: https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.KD
[14]: https://data.worldbank.org/indicator/NY.GDP.MKTP.PP.CD
[15]: https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.CD
[16]: https://ec.europa.eu/info/business-economy-euro/indicators-statistics/economic-databases/macro-economic-database-ameco/download-annual-data-set-macro-economic-database-ameco_en
[17]: http://atlas.cid.harvard.edu/downloads
[18]: https://atlas.media.mit.edu/en/resources/data/
[19]: https://data.worldbank.org/indicator/BN.CAB.XOKA.GD.ZS
[20]: https://data.worldbank.org/indicator/SP.POP.TOTL
[21]: https://stats.oecd.org/Index.aspx?DataSetCode=FIN_IND_FBS
[22]: https://data.worldbank.org/indicator/sl.ind.empl.zs
[23]: https://data.worldbank.org/indicator/SL.AGR.EMPL.ZS
[24]: https://data.worldbank.org/indicator/SL.SRV.EMPL.ZS
[25]: https://data.worldbank.org/indicator/SL.EMP.SELF.ZS
[26]: https://data.worldbank.org/indicator/SL.UEM.NEET.ZS
[27]: https://data.worldbank.org/indicator/NV.IND.TOTL.ZS
[28]: https://data.worldbank.org/indicator/NV.IND.MANF.ZS
[29]: https://info.worldbank.org/governance/wgi/#home
[30]: https://api.worldbank.org/v2/sources/3/indicators
[31]: https://data.worldbank.org/indicator/BX.KLT.DINV.WD.GD.ZS
[32]: https://data.worldbank.org/indicator/BM.KLT.DINV.WD.GD.ZS
[33]: https://data.worldbank.org/indicator/GC.TAX.TOTL.GD.ZS
[34]: https://data.worldbank.org/indicator/GC.TAX.INTT.RV.ZS
[35]: https://data.worldbank.org/indicator/GC.TAX.YPKG.RV.ZS
[36]: https://data.worldbank.org/indicator/NE.TRD.GNFS.ZS
[37]: https://data.worldbank.org/indicator/NE.EXP.GNFS.ZS
[38]: https://data.worldbank.org/indicator/NE.IMP.GNFS.ZS
[39]: https://data.worldbank.org/indicator/GB.XPD.RSDV.GD.ZS
[40]: https://data.worldbank.org/indicator/SP.POP.SCIE.RD.P6
[41]: https://stats.oecd.org/Index.aspx?DataSetCode=MEI_FIN
[42]: https://stats.oecd.org/Index.aspx?DataSetCode=AV_AN_WAGE
[43]: https://stats.oecd.org/Index.aspx?DataSetCode=NAAG
[44]: http://www.barrolee.com/

## Open issues

* Add more tests for duplicated rows, just as with AMECO


## Descriptive statistics
Here is more information about the data.
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
library(MacroDataR)
macro_data_descriptives <- macro_data %>%
  tidyr::gather(variable, value, -iso3c, -year) %>%
  group_by(variable) %>%
  summarise(mean=mean(value, na.rm=T),
            sd=sd(value, na.rm=T),
            obs=sum(!is.na(value))) %>%
  ungroup()
kable(macro_data_descriptives, caption = "The descriptive statistics")
```

# Information about the package

The package can be used to automatically update the whole dataset.
This way, it is straightforward to use newly published data.

To this end, you can use the function `update_macro_data`, which automatically recompiles the whole dataset.
See `help("update_macro_data", package = "MacroDataR")` for more details.
