---
title: "Macroeconomic data"
author: "Claudius Gräbner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Macroeconomic data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Information about the data set

## Meta data
Here goes the documentation of the data set. Note that you can also look at `data-raw/macro_data.R` to see how the data gets constructed.


| Variable         | Description                                  | Unit                          | Source           |
| -----------------|:--------------------------------------------:| :----------------------------:|:----------------:|
| iso3c                   | The iso3 country code                                                                                       | iso3c    | [Info][1] |
| year                    | The year of observation                                                                                     |   NA     |  |
| res_rents               | Natural ressource rents                                                                                     | % of GDP | [World Bank][2]
| gdp_real_lcu            | Real GDP in constant LCU                                                                                    | constant LCU | [World Bank][3]
| gdp_real_lcu_growth     | Real GDP growth (constant LCU)                                                                              | % change | [World Bank][2]
| gdp_real_pc_lcu         | Real GDP per capita (constant LCU)                                                                          | constant LCU per capita | [World Bank][2]
| gdp_real_pc_lcu_growth  | Real GDP per capita growth (constant LCU)                                                                   | % change | [World Bank][2]
| gdp_real_usd            | Real GDP (constant 2010 US$)                                                                                | constant 2010 US$ | [World Bank][2]
| gdp_real_pc_usd         | Real GDP per capita (constant 2010 US$)                                                                     | constant 2010 US$ per capita | [World Bank][2]
| gdp_nom_lcu             | Nominal GDP (current LCU)                                                                                   | current LCU | [World Bank][2]
| gdp_nom_pc_lcu          | Nominal GDP per capita (current LCU)                                                                        | current LCU per capita | [World Bank][2]
| gdp_nom_usd             | Nominal GDP (current US$)                                                                                   | current US$ | [World Bank][2]
| gdp_nom_pc_usd          | Nominal GDP per capita (current US$)                                                                        | current US$ per capita | [World Bank][2]
| gdp_real_ppp            | GDP, PPP (constant 2011 int $)                                                                              | constant 2011 int $ | [World Bank][2]
| gdp_real_pc_ppp         | GDP, PPP per capita (constant 2011 int $)                                                                   | constant 2011 int $ per capita | [World Bank][2]
| gdp_nom_ppp             | GDP, PPP (current int $)                                                                                    | current int $ | [World Bank][2]
| gdp_nom_pc_ppp          | GDP, PPP per capita (current int $)                                                                         | current int $ per capita | [World Bank][2]     
| cpi                     | Harmonised consumer price index (all items)                                                                 | 2015 = 100           | [AMECO][16]       |
| unemp_rate              | Unemployment rate                                                                                           | % of active population | [AMECO][16]     |
| cap_form                | Gross fixed capital formation, total economy                                                                | current prices       | [AMECO][16]       |
| wage_share              | Adjusted wage share                                                                                         | % of GDP             | [AMECO][16]       |
| rulc                    | Real unit labour costs: total economy (Ratio compensation per employee to nominal GDP per pers employed.)   | 2010=100             | [AMECO][16]       |
| nulc_nac                | Nominal unit labour costs: total economy (Ratio compensation per employee to real GDP per pers employed.)   | Loc curr: 2010 = 100 | [AMECO][16]       |
| nulc_eur                | Nominal unit labour costs: total economy (Ratio compensation per employee to real GDP per pers employed.)   | EUR: 2010 = 100      | [AMECO][16]       |


[1]: https://unstats.un.org/unsd/tradekb/knowledgebase/country-code
[2]: https://data.worldbank.org/indicator/ny.gdp.totl.rt.zs
[3]: https://data.worldbank.org/indicator/NY.GDP.MKTP.KN
[4]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KN
[5]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KD.ZG
[6]: https://data.worldbank.org/indicator/NY.GDP.MKTP.KD
[7]: https://data.worldbank.org/indicator/NY.GDP.PCAP.KD
[8]: https://data.worldbank.org/indicator/NY.GDP.MKTP.CN
[9]: https://data.worldbank.org/indicator/NY.GDP.PCAP.CN
[10]:https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
[11]: https://data.worldbank.org/indicator/NY.GDP.PCAP.CD
[12]: https://data.worldbank.org/indicator/NY.GDP.MKTP.PP.KD
[13]: https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.KD
[14]: https://data.worldbank.org/indicator/NY.GDP.MKTP.PP.CD
[15]: https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.CD
[16]: https://ec.europa.eu/info/business-economy-euro/indicators-statistics/economic-databases/macro-economic-database-ameco/download-annual-data-set-macro-economic-database-ameco_en

## Open issues

* Fix units for new World Bank data
* Where did **Current account balance to GDP' come from** It says AMECO, but I could not find it.
* Where did **Public debt to GDP** come from? It says AMECO, but I could not find it.
* Add more tests for duplicated rows, just as with AMECO


## Descriptive statistics
Here is more information about the data.
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
library(MacroDataR)
macro_data_descriptives <- macro_data %>%
  tidyr::gather(variable, value, -iso3c, -year) %>%
  group_by(variable) %>%
  summarise(mean=mean(value, na.rm=T),
            sd=sd(value, na.rm=T),
            obs=sum(!is.na(value))) %>%
  ungroup()
kable(macro_data_descriptives, caption = "The descriptive statistics")
```

# Information about the package

The package can be used to automatically update the whole dataset.
This way, it is straightforward to use newly published data.

To this end, you can use the function `update_macro_data`, which automatically recompiles the whole dataset.
See `help("update_macro_data", package = "MacroDataR")` for more details.
