---
title: "Macroeconomic data"
author: "Claudius Gräbner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Macroeconomic data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Information about the data set

## Meta data
Here goes the documentation of the data set. Note that you can also look at `data-raw/macro_data.R` to see how the data gets constructed.


| Variable      | Description                | Unit     | Source     |
| ------------- |:--------------------------:| :-------:|:----------:|
| iso3c         | The iso3 country code      | iso3c    | [Link][1]  |
| year          | The year of observation    |   NA     |            |
| res_rents     | Natural ressource rents    | % of GDP | [Link][2]  |

[1]: https://unstats.un.org/unsd/tradekb/knowledgebase/country-code
[2]: https://data.worldbank.org/indicator/ny.gdp.totl.rt.zs

## Descriptive statistics
Here is more information about the data.
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
library(MacroDataR)
macro_data_descriptives <- macro_data %>%
  tidyr::gather(variable, value, -iso3c, -year) %>%
  group_by(variable) %>%
  summarise(mean=mean(value, na.rm=T),
            sd=sd(value, na.rm=T),
            obs=n()) %>%
  ungroup()
kable(macro_data_descriptives, caption = "The descriptive statistics")
```

# Information about the package

The package can be used to automatically update the whole dataset.
This way, it is straightforward to use newly published data.

To this end, you can use the function `update_macro_data`, which automatically recompiles the whole dataset.
See `help("update_macro_data", package = "MacroDataR")` for more details.
